ESRC SDAI Application

### 2019-06-19 case_for_support.tex
Anna update

>>>>

Using data from the CSEW and well as population data of the West Midlands, we can estimate how many children and young people below 18 in each LSOA of the West Midlands are at risk of witnessing domestic abuse at home each year.

\textit{The problem is that we don't know the address of the young offenders. Could we the location info on where they committed the offences as a proxy of the LSOA where they live? not sure if this is viable;
defining a gang member is problematic in the crime data - if something serious is committed probably only one of them will be charged with it;
I was trying to identify children who were victims of something happening at an address where DA happened and perpetrated by a DA offender - it's very narrow and excludes children who *just* witnessed abuse}
